On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-25 4_Result.tex
review of the survey results

\subsection{Misunderstanding Analysis}

@@

As mentioned in Section~\ref{sec:meth:survey}, each participant in this study evaluated ten.
%code snippets, from which five were in their confusing versions, whilst the other five contained cleaned versions of the code snippets (i.e., without the confusing constructs and idioms). 
The participants should provide the expected outcomes of the code snippets. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{cognitive workload} (the time taken to answer the question). 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness.

@@

\begin{table*}[htbp]
\caption{Total number of correct answers.}
\label{tab:difference-correctness}
\centering{
\begin{tabular}{lccc|c} \toprule
 % & \multicolumn{2}{c}{Total Number of Correct Answers} & \\ [0.1cm]
  Atom & Confusing Code & Clean Code & $\Delta$(\%) & Effect Size (Odds Ratio) \\ \midrule
  Comma Operator &  28 &  65 & +132 & 19.02 \\ 
%   {\color{red}Automatic Semicolon Insertion} &  32 &  68 & +112 & 39.32 \\ 
  Post Increment &  48 &  64 & +33 & 4.83 \\ 
  Omitted Curly Braces &  47 &  58 &  +23 & 2.35 \\
  Assignment as Value &  56 &  68 &  +21 & 8.38 \\ 
  Implicit Predicate &  58 &  68 &  +17 & 6.94 \\ 
  Logic as Control Flow &  41 &  48 &  +17 & 1.53 \\ 
  Ternary Operator &  60 &  66 &  +10 & 2.73 \\ 
  Pre-Increment &  50 &  53 &  +6 & 1.24 \\ 
  Arithmetic as Logic &  64 &  63 &  -2 & 0.84 \\ \bottomrule 
\end{tabular}
}
\end{table*}

@@

We first use the \emph{Pearson's Chi-squared test}
to investigate if there is a statistically significant difference
in the frequency of correct and incorrect answers---due to the versions
of the code snippets (confusing and clean code). The result indicates that the confusing versions of the code snippets have a negative impact on code understanding (p-value $< 0.05$). We also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant
\emph{education} or participant \emph{experience} impact correctness. Although the results suggest that experience impacts correctness, the education level does not. As such, we replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistical difference is less significant for those developers with more than ten years of experience.
Finally, we measure the effect size of the clean version of the code snippets into the answers' correctness, using the \emph{Odds Ratio} (OR)
method (see the Effect Size column of Table~\ref{tab:difference-correctness}). We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and
Pre-Increment. Nonetheless, for the remaining candidates, the effect size is significant. For instance, the Comma Operator leads to an \emph{Odds Ratio} of
\num{19.02}, meaning that the the odds of a correct answer are \num{19.02} times
higher when interpreting the clean version of a code---in comparison with the corresponding, confusing version of the code snippet.

@@

% \begin{table*}[htbp]
% \caption{Time in seconds to submit a correct answer}
% \label{tab:difference-time-taken}
% \centering{
% \begin{tabular}{lccc|cc} \toprule
% Atom & Confusing Code & Clean Code & $\Delta$(\%) & Mann-Whitney test & Cliff's Delta \\ \midrule 
% Comma Operator & 87.67 & 20.84 & -76.23 &  \colorbox{lightgray}{$<$ 0.01} & -0.53 \\ 
% Logic as Control Flow & 108.94 & 51.07 & -53.12 &  \colorbox{lightgray}{$<$ 0.01} & -0.39 \\ 
% % {\color{red}Automatic Semicolon Insertion} & 46.08 & 22.04 & -52.17 & 0.09 & -0.16 \\ 
% Omitted Curly Braces & 48.85 & 30.00 & -38.58 & 0.92 & -0.01 \\ 
% Implicit Predicate & 36.24 & 24.01 & -33.75 & \colorbox{lightgray}{$<$ 0.01} & -0.29 \\ 
% Post Increment & 28.70 & 25.67 & -10.56 & 0.12 & 0.15 \\ 
% Assignment as Value & 52.47 & 48.95 & -6.71 & 0.82 & 0.02 \\ 
% Ternary Operator & 41.80 & 39.34 & -5.90 & 0.24 & -0.12 \\ 
% Arithmetic as Logic & 28.82 & 37.20 & +29.06 & \colorbox{lightgray}{0.01} & 0.23 \\ 
% Pre-Increment & 30.71 & 42.45 & +38.19 & \colorbox{lightgray}{$<$ 0.01} & 0.27 \\ 
%          \bottomrule
%     \end{tabular}}
% \end{table*}

 % latex table generated in R 4.0.4 by xtable 1.8-4 package
 % Thu Apr 22 07:58:21 2021
 \begin{table*}[ht]
\caption{Time in seconds to submit a correct answer}
\label{tab:difference-time-taken}

 \centering
 \begin{tabular}{rllrlrrlr}
   \hline
  & Atom & ChiTest & Odds Ratio Correctness & p-value & CI 2.5\% & CI 97.5\% & Wilcox Test (Time) & Cliff Delta \\ 
   \hline
 3 & Automatic Semicolon Insertion & 5.8352e-11 & 39.33 & 2.4351e-12 & 9.21 & 356.62 & 0.09802 & -0.16 \\ 
   4 & Comma Operator & 1.1727e-10 & 19.02 & 1.5812e-11 & 6.60 & 68.22 & 5.8249e-08 & -0.53 \\ 
   2 & Assignment as Value & 0.0034775 & 8.39 & 0.0024331 & 1.81 & 79.12 & 0.82681 & 0.02 \\ 
   6 & Implict Predicate & 0.01123 & 6.95 & 0.008974 & 1.46 & 66.56 & 0.0029039 & -0.29 \\ 
   9 & Post Increment & 0.0015279 & 4.83 & 0.0012328 & 1.73 & 15.74 & 0.12006 & 0.15 \\ 
   5 & Ternary Operator & 0.15896 & 2.73 & 0.15712 & 0.74 & 12.57 & 0.24073 & -0.12 \\ 
   8 & Ommitted Curly Braces & 0.050962 & 2.35 & 0.050056 & 1.00 & 5.77 & 0.92529 & -0.01 \\ 
   7 & Logic as Control Flow & 0.292 & 1.54 & 0.29198 & 0.73 & 3.28 & 7.5862e-05 & -0.39 \\ 
   10 & Pre Increment & 0.70147 & 1.25 & 0.70181 & 0.55 & 2.85 & 0.0062981 & 0.27 \\ 
   1 & Arithmetic as Logic & 1 & 0.84 & 1 & 0.22 & 3.12 & 0.01723 & 0.23 \\ 
    \hline
 \end{tabular}
 \end{table*}

\subsubsection*{Hypothesis Testing}
We use the non-parametric \emph{Mann-Whitney U test}, also known as Wilcoxon rank-sum test, to
investigate the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of a code snippet, regardless
of evaluating the confusing or  clean version
of the code. The results of Table~\ref{tab:difference-time-taken}
suggest that we should refute the null hypotheses for
five atom candidates (Comma Operator, Logic
as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre-Increment). This result holds even after applying the Benjamini-Hochberg correction with a false discovery rate of 5\%. 
For the first three, the analysis suggests that the participants
need more time to predict the outcome of
the code snippet in the confusing code version. Interesting,
for the atom candidates Arithmetic as Logic and
Pre-Increment, the participants take less time
to predict the outcome of the code snippets in
the confusing version.
We also computed the effect size using the Cliff's Delta method.
We found a large effect for the Comma Operator atom
candidate; and a moderate effect for the atom candidates
Logic as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre-Increment.

\begin{mh}
  The results suggest that developers spend
  significantly more time to predict the
  correct answer in the presence of the
  atom candidates Comma Operator, Logic as
  Control Flow, and Implicit Predicate. Conversely,
  the version of the code snippets with the
  atom candidates Arithmetic as Logic and
  Pre-Increment demands less time to
  predict the correct answers. 
\end{mh}

>>>>

\subsection{Misunderstanding Rate Analysis}

@@

As mentioned in Section~\ref{sec:meth:survey}, each participant in this study evaluated ten
code snippets, from which five were in their confusing versions, whilst the other five contained cleaned versions of the
code snippets (i.e., without the confusing constructs and idioms). 
The participants should provide the expected outcomes of the code snippets. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{cognitive workload} (the time taken to answer the question). 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness.

@@

\begin{table}[htbp]
\caption{Total number of correct answers.}
\label{tab:difference-correctness}
\centering{
\begin{scriptsize}
\begin{tabular}{lccc} \toprule
  Atom & Confusing Code & Clean Code & $\Delta$(\%)  \\ \midrule
  Comma Operator                &  28 &  65 & +132   \\ 
  Automatic Semicolon Insertion &  32 &  68 & +112   \\ 
  Post-Increment                &  48 &  64 & +33    \\ 
  Omitted Curly Braces          &  47 &  58 &  +23   \\
  Assignment as Value           &  56 &  68 &  +21   \\ 
  Implicit Predicate            &  58 &  68 &  +17   \\ 
  Logic as Control Flow         &  41 &  48 &  +17   \\ 
  Ternary Operator              &  60 &  66 &  +10   \\ 
  Pre-Increment                 &  50 &  53 &  +6    \\ 
  Arithmetic as Logic           &  64 &  63 &  -2    \\ \bottomrule

\end{tabular}
\end{scriptsize}
}
\end{table}

@@

We first use the \emph{Pearson's Chi-squared test}
to investigate if there is a statistically significant difference
in the frequency of correct and incorrect answers---due to the versions
of the code snippets (confusing and clean code). The result indicates that the confusing versions of the code snippets have a negative impact on code understanding (p-value $< 0.05$). We also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant
\emph{education} or participant \emph{experience} impact correctness. Although the results suggest that experience impacts correctness, the education level does not. As such, we replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistical difference is less significant for those developers with more than ten years of experience.
Finally, we measure the effect size of the clean version of the code snippets into the answers' correctness, using the \emph{Odds Ratio} (OR)
method (see the Odds Ratio column of Table~\ref{tab:hypothesis-testing}). We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and
Pre-Increment. Nonetheless, for the remaining candidates, the effect size is significant. For instance, the Comma Operator leads to an \emph{Odds Ratio} of
\num{19.02}, meaning that the the odds of a correct answer are \num{19.02} times
higher when interpreting the clean version of a code---in comparison with the corresponding, confusing version of the code snippet.

@@

\begin{table}[htbp]
\caption{Time in seconds to submit a correct answer}
\label{tab:difference-time-taken}
\centering{
\begin{scriptsize}
\begin{tabular}{lccc} \toprule
Atom & Confusing Code & Clean Code & $\Delta$(\%) \\ \midrule
Comma Operator & 87.67 & 20.84 & -76.23 \\ 
Automatic Semicolon Insertion & 46.08 & 22.04 & -52.17 \\ 
Post-Increment & 28.70 & 25.67 & -10.56 \\ 
Ommitted Curly Braces & 48.85 & 30.00 & -38.58 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 \\ 
Implict Predicate & 36.24 & 24.01 & -33.75 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 \\ 
Ternary Operator & 41.80 & 39.34 & -5.90 \\ 
Pre-Increment & 30.71 & 42.45 & 38.19 \\  
Arithmetic as Logic & 28.82 & 37.20 & 29.06 \\ \bottomrule
\end{tabular}
\end{scriptsize}
}
\end{table}

 % latex table generated in R 4.0.4 by xtable 1.8-4 package
 % Thu Apr 22 07:58:21 2021
 \begin{table*}[ht]
\caption{Hipothesis Testing (misunderstanding and cognitive workload)}
\label{tab:hypothesis-testing}

 \centering
 \begin{tabular}{lcccc|cc}
   \toprule
Atom & ChiTest & Odds Ratio          & CI 2.5\% & CI 97.5\% & Wilcox Test & Cliff Delta \\ 
     &         & (misunderstanding)  &          &           & (workload)             & \\ \midrule
Comma Operator & 1.1727e-10 & 19.02 & 6.60 & 68.22 & 5.8249e-08 & -0.53 \\ 
Automatic Semicolon Insertion & 5.8352e-11 & 39.33 & 9.21 & 356.62 & 0.09802 & -0.16 \\ 
Post-Increment & 0.0015279 & 4.83 & 1.73 & 15.74 & 0.12006 & 0.15 \\ 
Ommitted Curly Braces & 0.050962 & 2.35 & 1.00 & 5.77 & 0.92529 & -0.01 \\ 
Assignment as Value & 0.0034775 & 8.39 & 1.81 & 79.12 & 0.82681 & 0.02 \\ 
Implict Predicate & 0.01123 & 6.95 & 1.46 & 66.56 & 0.0029039 & -0.29 \\ 
Logic as Control Flow & 0.292 & 1.54 & 0.73 & 3.28 & 7.5862e-05 & -0.39 \\ 
Ternary Operator & 0.15896 & 2.73 & 0.74 & 12.57 & 0.24073 & -0.12 \\ 
Pre-Increment & 0.70147 & 1.25 & 0.55 & 2.85 & 0.0062981 & 0.27 \\ 
Arithmetic as Logic & 1 & 0.84 & 0.22 & 3.12 & 0.01723 & 0.23 \\ 
    \bottomrule
 \end{tabular}
 \end{table*}

\subsubsection*{Hypothesis Testing}
We use the non-parametric \emph{Mann-Whitney U test}, also known as Wilcoxon rank-sum test, to
investigate the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of a code snippet, regardless
of evaluating the confusing or  clean version
of the code. The results of Table~\ref{tab:difference-time-taken}
suggest that we should refute the null hypotheses for
six atom candidates (Comma Operator, Automatic Semicolong Insertion,
Implicit Predicate, Logic
as Control Flow, Pre-Increment, and Arithmetic
as Logic). This result holds even after applying the Benjamini-Hochberg correction with a false discovery rate of 5\%. 
For the first four, the analysis suggests that the participants
need more time to predict the outcome of
the code snippet in the confusing code version. Interesting,
for the atom candidates Arithmetic as Logic and
Pre-Increment, the participants take less time
to predict the outcome of the code snippets in
the confusing version.
We also computed the effect size using the Cliff's Delta method.
We found a large effect for the Comma Operator atom
candidate; and a moderate effect for the atom candidates
Logic as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre-Increment.

\begin{mh}
  The results suggest that developers spend
  significantly more time to predict the
  correct answer in the presence of the
  atom candidates Comma Operator, Automatic Semicolon Insertion, Logic as
  Control Flow, and Implicit Predicate. Conversely,
  the version of the code snippets with the
  atom candidates Arithmetic as Logic and
  Pre-Increment demands less time to
  predict the correct answers. 
\end{mh}
